---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}
library(ggplot2)
library(palmerpenguins)
head(penguins)
```



```{r}
ggplot(data = penguins)+
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g))
```

```{r}
data("diamonds")
head(diamonds)
```

```{r}
ggplot(data = diamonds)+geom_bar(mapping = aes(x = cut))
```


```{r}
ggplot(data = penguins)+geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g))
```
The plot shows a
positive relationship between the two variables. In other words, the
larger the penguin, the longer the flipper.


```{r}
ggplot(data = penguins, aes(x = bill_length_mm, y = bill_depth_mm))+geom_point()
```


```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species))+
  geom_point()
```
The Gentoo are the largest of
the three penguin species. The legend just to the right of the plot
shows us that the blue points refer to the Gentoo penguins.

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g, shape = species))+
  geom_point()
```


```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species, shape = species))+
  geom_point()
```

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species, shape = species, size = species))+
  geom_point()
```

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g, alpha = species))+
  geom_point()
```

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g))+
  geom_point(alpha = 0.5)
```

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g))+
  geom_point(color = "purple")
```

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g))+
  geom_smooth(color = "purple")

```
The geom underscore
smooth function's useful for showing general
trends in our data. The line clearly shows the positive relationship between body mass and flipper length. The larger the penguin, the longer the flipper. We can even use two
geoms in the same plot. Let's say we want to show
the relationship between the trend line and the
data points more clearly. We can combine the code for geom underscore point and the code for geom
underscore smooth by adding a plus symbol after
geom underscore smooth


```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g))+
  geom_smooth(color = "purple")+geom_point()

```

```{r}
ggplot(data = penguins ) + 
  geom_smooth(mapping = aes(x = flipper_length_mm, y = body_mass_g, linetype = species))
```
 The geom underscore
jitter function creates a scatter plot and then adds a small amount of random noise to each
point in the plot. Jittering helps us deal
with over-plotting, which happens when
the data points in a plot overlap with each other. Jittering makes the
points easier to find.
```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g))+
  geom_jitter()
```

```{r}
ggplot(data = diamonds, aes( x = cut))+geom_bar()
```

When you use geom underscore bar, R automatically counts how many times each x-value
appears in the data, and then shows the
counts on the y-axis. The default for geom underscore
bar is to count rows.


```{r}
ggplot(data = diamonds, aes( x = cut, color = cut))+geom_bar()
```

```{r}
ggplot(data = diamonds, aes( x = cut, fill = cut))+geom_bar()
```
```{r}
ggplot(data = diamonds, aes( x = cut, fill = clarity))+geom_bar()+
```


```{r}
ggplot(data = diamonds, aes( x = cut, fill = clarity))+geom_bar()+
  facet_wrap(~clarity)+
  theme(axis.text.x = element_text(angle = 45))
```

Facet allows you to display smaller groups, or subset of your data
facet_wrap for single variable
facet_grid for two variables

```{r}
ggplot(data = diamonds, aes( x = color, fill = cut))+geom_bar()+
  facet_wrap(~cut)+
  theme(axis.text.x = element_text(angle = 45))
```



```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species))+
  geom_point()+facet_grid(~sex~species)
```

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species))+
  geom_point()+facet_grid(~species)
```

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species))+
  geom_point()+facet_grid(~sex)
```
Annotation

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species))+
  geom_point()+ 
  labs(title = "Palmer Penguins: Body Mass vs Flipper Length")

```

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species))+
  geom_point()+ 
  labs(title = "Palmer Penguins: Body Mass vs Flipper Length", subtitle = "Sample of Three Penguin Species")

```
```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species))+
  geom_point()+ 
  labs(title = "Palmer Penguins: Body Mass vs Flipper Length", subtitle = "Sample of Three Penguin Species", caption = "Data collected by Dr Kisten Gorman")
```

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species))+
  geom_point()+ 
  labs(title = "Palmer Penguins: Body Mass vs Flipper Length", subtitle = "Sample of Three Penguin Species")+annotate("text", x = 220, y = 3500, label = "The Gentoos are the largest", color = "purple",fontface = "bold", size = 4.5, angle = 25)
```

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species))+
  geom_point()
```

```{r}
ggsave("Three Penguins Species.png")
```

```{r}
ggplot(data = penguins) + 
     geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g, size = species))
```

